\chapter*{Acknowledgments}
The completion of this thesis could not have been possible without the help of my first examiner Prof.~Dr.~Michael Lehmann, whom I would like to sincerely thank for all the great scientific discussions we had as well as the opportunity to use his excellent laboratory.

My deepest gratitude goes to my supervisor Dr.~Tolga Wagner, who has accompanied me, both personally and scientifically, on this journey from the very beginning.

I would like to thank Dr.~Andrei Schliwa for assuming the role as second examiner, for his help with acquiring a license for the \emph{nextnano} software package and for all the productive scientific discussions we had.

I am sincerely grateful to my friend and colleague Robert Fuchs, without whose valuable discussions the mathematical foundation of \emph{SIMP} would never have come about.

I owe a debt of gratitude to my esteemed colleague Dr.~Ines Häusler from the Humboldt University of Berlin for providing me with the CBED measurement data and analysis of the $p$-$p^+$-$n^+$-junction.

Furthermore, I would like to thank my entire work group, especially Elke Wandke, for the warm reception I received from the very beginning.

I am thankful to the members of the ZELMI of the Technische Universität Berlin, especially Dr.~Christian Günther and Dr.~Dirk Berger, for providing me with the specimens and a pleasant work environment in the laboratory.

I also thank Henrik Wähnert, Jan Simke and Dr.~Nina Owschimikow for the sometimes much needed distraction and all the great conversations we had.

At last, my deepest gratitude goes to my parents Dürdane and Ali Çelik, who have given me the opportunity to pursue this degree.
